\documentclass[11pt,letterpaper, sans]{moderncv}

% ModernCV Theme
\moderncvtheme[green]{classic}

% Character Encoding
\usepackage[utf8]{inputenc}

% Adjust the page margins
\usepackage[scale=0.85]{geometry}
\recomputelengths

% Suppress page numbers
\nopagenumbers

% Personal Info
\firstname{Gaelan}
\familyname{D\kern-.05em'\kern-.1emcosta}
\address{79 Broadview Avenue}{Toronto, ON, Canada, M4M 2E4}
\mobile{416--527--1802}
\email{gdcosta@gmail.com}
\extrainfo{\httplink{www.github.com/NaleagDeco}}

\begin{document}
\maketitle

%\section{Objective}
%\cvline{}{A leadership software role within Toronto's Agile Development.}

\section{Languages}
\cvlanguage{}{Fluent}{C++, JavaScript, Python, Ruby}
\cvlanguage{}{Intermediate}{C, Java, Common Lisp/Scheme, HTML, Scala,
  Shell Scripting, SQL}
\cvlanguage{}{Familiar}{Clojure, \LaTeX, Haskell}

\section{Skills}
\cvlistdoubleitem{Code Quality Metrics}{Agile Planning Methodology}
\cvlistdoubleitem{Test Driven Development}{Multi-paradigm Programming}
\cvlistdoubleitem{Web-application Bootstrapping}{Virtualized
  Development Environments}
\cvlistdoubleitem{Mentoring}{Team Leadership}
\cvlistdoubleitem{Master Data Management}{ETL}
\cvlistdoubleitem{Field Troubleshooting}{Requirements Development}
\cvlistdoubleitem{Concurrency Primitives}{Operating System Multiprocessing}

\section{Experience}
\cventry{2013--2014}{Senior Software Development}{Gallop Labs}{Toronto, ON}{}{
  \begin{itemize}
    \item Refactored a Django \& AngularJS web application from a
      Facebook Ad Campaign editor into a platform for automated
      analysis of Facebook advertisements and mobile user events.
    \item Engineered a Couchbase-driven service that stored historical
      Facebook ad performance in hourly increments for analysis, though
      Facebook's API only provides daily aggregates.
    \item Used various open source libraries, to replace custom
      modules for integrating with external services, contributing
      functionality when required.
    \item When requiring a proof-of-concept for automated campaign
      optimization, consulted with external data scientists, to
      provide a solution using Python scientific and decision trees.
    \item Given a young team without much organizational experienced,
      collaborated with business development to form processes for converting
      business requirements into roadmaps, technical designs and user stories.
      % while moving at bootstrapped company speeds.
  \end{itemize}
}
\cventry{2011--2013}{Business Infrastructure
  Engineer}{Kontagent}{Toronto, ON}{Python, Salesforce}{
  \begin{itemize}
  \item Designed an automated infrastructure for producing usage,
    sales and churn metrics from company's Django-derived platform,
    delivering and displaying results into Salesforce dashboards.
  \item Reworked development environment from one requiring manual
    management of multiple Xen-based instances into an environment
    run on developer machines via Vagrant and configured via Salt (a
    Chef/Puppet alternative) using Vagrant for virtualization and Salt
    for automatic configuration.
  \item Developed platform for automatically generating customer
    documentation APIs from engineering-defined schemas.
  \item Developed Sales Force Automation functionality using
    Salesforces' custom classes and triggers.
  % \item Engaged local developer community in order to attract talent
  %   and increase Kontagent's presence in community.
  \end{itemize}
}
\cventry{2010--2011}{Infrastructure Engineer}{Blue Coat
  Systems}{Waterloo, ON}{C++, DSLs}{
  \begin{itemize}
  \item Ported the open-source PCRE regular expression library to a
    system with
    no global heaps, fixed stack memory limits and no virtual memory protection.
  \item Restructured monolithic and inadequately-tested components
    into well-tested modular designs.
  \item Adopted --- organically and through retrospection --- scrum
    and test-driven methodologies for a team with a variety of
    experience and enthusiasm.
  \end{itemize}
}
\cventry{2006--2010}{Intern/Sustaining Engineer}{Blue Coat Systems}{Waterloo,
  ON}{C++, embedded operating systems}{
  \begin{itemize}
  \item Diagnosed memory dumps from crashed network devices, delving
    into semi-familiar codebases to fix errors in:
    \begin{itemize}
    \item optimized binaries with or without debugger support and annotated
      assembly listings
    \item hardware defects
    \item application-specific protocol optimization.
    \item configuration language parsing and compilation.
    \item interprocess communication primitives and concurrency mechanisms.
    \item core kernel routines.
    \item log-based filesystem operations.
    \end{itemize}
  \item Trended internal crash statistics to proactively anticipate
    possible issues in the field.
  \item Developed custom continuous integration system to poll source
    repositories for new changes to test and deploy.
  \end{itemize}
}
\cventry{2005}{Co-op Software Engineer}{Community Care Access Centre}{Kitchener,
  ON}{Tomcat, Java, SQL}{
  \begin{itemize}
    \item Frontend and backend development of a PIPEDA-compliant
      document exchange platform used province-wide by Ontario long-term
      healthcare providers.
    \item Contributed 80\% of product's code modifications during
      tenure of work term.
    \item Leveraged user feedback and independent research to refine
      platform UX/UI.
    \item Despite being student employee, proposed future directions
      and led design discussions around those proposals.
  \end{itemize}}
\cventry{2003--2005}{Previous Co-op Experience}{Available on Request}{}{}{}

\section{Education}
\cventry{2002--2007}{Computer Science with Philosophy minor}{University of
  Waterloo}{}{}{}

\section{Extracurricular}
\cventry{2014}{Random Hacks of Kindness}{}{Digital Books of
  Authority}{}{
  \begin{itemize}
  \item HTML5 application enabling lawyers to automatically create court
    filings
  \item Document generation and precedence citing via templates and
    API access to the Canadian Legal Information Institute's
    document archive.
  \end{itemize}}
\cventry{2013}{Backend/REST API development}{NASA Space
  Apps}{Waystation (Toronto finalist)}{}{
  \begin{itemize}
  \item Displayed the International Space Station's location over the
    Earth in realtime
  \item REST backend --using Python/Flask-- for facilitating
    interaction with ISS astronauts via Twitter and online
    photographs.
  \end{itemize}}
\cventry{2013}{Participant}{Global Game Jam: Games for Change}{Common
  Causes}{}{Physical board game highlighting the challenges and
  tradeoffs in allocating limited resources to social causes.}
\cventry{2011}{Open Data Waterloo Region}{}{}{}{}
\cventry{2009}{Exhibit Operations Volunteer}{Contemporary Art Festival
  of Kitchener + Area}{}{}{}
\cventry{2008}{Scriptwriter}{University of Waterloo Faculty, Alumni, Student
  and Staff Theatre Company}{}{}{}{}
\cventry{2007}{President}{UW Undergraduate Computer Science Club}{}{}{
  Approached and facilitated public lectures by Bjarne Stroustrup and
  Richard M. Stallman on behalf of the University of Waterloo.}
\end{document}
